DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-08-16 ase2017/paper.tex
font consistency

The first approach, presented in Fig.~\ref{fig:CEGIS-precision-increment}, 
uses a multi-staged verification process. 
It starts by devising a digital controller that stabilizes the model while remaining safe for a
pre-selected time horizon ($k$) and a single initial state; then, it
employs a multi-staged verification process as follows:
(i) The first verification stage ({\sc safety}) checks that the candidate
solution, which we synthesized to be safe for at least one initial
state, is safe for \emph{all} possible initial states, i.e., does not reach
an unsafe state within $k$ steps.
(ii) The second verification stage ({\sc precision})
 restores soundness with respect to the plant precision
by using interval arithmetic \cite{moore1966interval} to validate the 
operations performed by the previous stage. 
(iii) The third verification stage ({\sc complete}) checks that the current
$k$ is large enough to ensure safety for any $k'{>}k$.  Here, we compute the
completeness threshold $\overline{k}$ for the current candidate controller 
$K$~\cite{abatecav2017}, i.e., the number of
iterations required to sufficiently unwind the closed-loop state-space
model such that the boundaries are not violated for any larger number of
iterations, and
check that $k{\geq}\overline{k}$.
%
\begin{figure}
\centering
{\scriptsize
  \resizebox{.5\textwidth}{!}
  {
\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center},row sep=.8cm, column sep=.2cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \& ;\\
   \&\node[fill=gray!20,align=center,xshift=-1.5cm] (pre) {{\sc 1. pre-}\\{\sc processing}};
   \& \node[fill=gray!20,align=center] (abstract) {\sc 4. abstract};
   \& \coordinate (aux); \\ 
   \&
   \& \node[fill=gray!20,align=center] (synth) {\sc 2. synthesize};
   \& \node[fill=gray!20,align=center, minimum width=4cm] (verify) {\sc 3. verify ($\phi$)};
      \node[draw=none] (SAT) at ([xshift=2.7cm,yshift=-.3cm]verify)  {\sc PASS};
   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
   \&
   \& \node[draw,rectangle,align=center] (KSAT) {Program \\ Search};
   \& complexnode/.pic={
     \coordinate (AA);
     \node[draw,rectangle,align=center] (AAV) at ([xshift=-1.5cm]AA.center) {Abstract\\Acceleration};
     \node[draw,rectangle,align=center] (AAC) at ([xshift=1.5cm]AA.center) {Abstraction \\ Verifier};
    }\\
  };
  \path
    (pre.east) edge node[align=center] {} (abstract.west)
    (abstract.south) edge node{} (synth.north)
    ([yshift=1em]synth.east) edge node {$K$} ([yshift=1em]verify.west)
    (aux) edge (abstract.east) 
    (verify.east) edge (done.west);
  \path
    ([xshift=+.6cm]KSAT.north) edge[left] node[xshift=-.3cm] {} ([xshift=0.6cm]synth.south) 
    ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {} ([xshift=-.6cm]KSAT.north)
    ([yshift=.5cm]AAV.east) edge node{} ([yshift=.5cm]AAC.west)
    ([yshift=-.5cm]AAC.west) edge node{} ([yshift=-.5cm]AAV.east)
    (AAC.north) edge node{} ([xshift=4.9cm]verify.south)
    ([xshift=-5cm]verify.south) edge node{} (AAV.north);
  \path[-] 
     (verify.north) edge node {C-ex} (aux);
\end{tikzpicture}
}
}
\caption{Abstraction-based CEGIS}
\label{fig:CEGARIS} 
\end{figure}

>>>>

The first approach, presented in Fig.~\ref{fig:CEGIS-precision-increment}, 
uses a multi-staged verification process. 
It starts by devising a digital controller that stabilizes the model while remaining safe for a
pre-selected time horizon ($k$) and a single initial state; then, it
employs a multi-staged verification process as follows:
(i) The first verification stage ({\sc safety}) checks that the candidate
solution, which we synthesized to be safe for at least one initial
state, is safe for \emph{all} possible initial states, i.e., does not reach
an unsafe state within $k$ steps.
(ii) The second verification stage ({\sc precision})
 restores soundness with respect to the plant precision
by using interval arithmetic \cite{moore1966interval} to validate the 
operations performed by the previous stage. 
(iii) The third verification stage ({\sc complete}) checks that the current
$k$ is large enough to ensure safety for any $k'{>}k$.  Here, we compute the
completeness threshold $\overline{k}$ for the current candidate controller 
$K$~\cite{abatecav2017}, i.e., the number of
iterations required to sufficiently unwind the closed-loop state-space
model such that the boundaries are not violated for any larger number of
iterations, and
check that $k{\geq}\overline{k}$.
%
\begin{figure}
\centering
{\scriptsize
  \resizebox{.5\textwidth}{!}
  {
\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center},row sep=.8cm, column sep=.2cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \& ;\\
   \&\node[fill=gray!20,align=center,xshift=-1.5cm] (pre) {{\sc 1. pre-}\\{\sc processing}};
   \& \node[fill=gray!20,align=center] (abstract) {\sc 4. abstract};
   \& \coordinate (aux); \\ 
   \&
   \& \node[fill=gray!20,align=center] (synth) {\sc 2. synthesize};
   \& \node[fill=gray!20,align=center, minimum width=4cm] (verify) {\sc 3. verify ($\phi$)};
      \node[draw=none] (SAT) at ([xshift=2.7cm,yshift=-.3cm]verify)  {\sc PASS};
   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
   \&
   \& \node[draw,rectangle,align=center] (KSAT) { \sf Program \\ \sf Search};
   \& complexnode/.pic={
     \coordinate (AA);
     \node[draw,rectangle,align=center] (AAV) at ([xshift=-1.5cm]AA.center) { \sf Abstract\\ \sf Acceleration};
     \node[draw,rectangle,align=center] (AAC) at ([xshift=1.5cm]AA.center) { \sf Abstraction \\ \sf Verifier};
    }\\
  };
  \path
    (pre.east) edge node[align=center] {} (abstract.west)
    (abstract.south) edge node{} (synth.north)
    ([yshift=1em]synth.east) edge node {$K$} ([yshift=1em]verify.west)
    (aux) edge (abstract.east) 
    (verify.east) edge (done.west);
  \path
    ([xshift=+.6cm]KSAT.north) edge[left] node[xshift=-.3cm] {} ([xshift=0.6cm]synth.south) 
    ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {} ([xshift=-.6cm]KSAT.north)
    ([yshift=.5cm]AAV.east) edge node{} ([yshift=.5cm]AAC.west)
    ([yshift=-.5cm]AAC.west) edge node{} ([yshift=-.5cm]AAV.east)
    (AAC.north) edge node{} ([xshift=4.9cm]verify.south)
    ([xshift=-5cm]verify.south) edge node{} (AAV.north);
  \path[-] 
     (verify.north) edge node {C-ex} (aux);
\end{tikzpicture}
}
}
\caption{Abstraction-based CEGIS}
\label{fig:CEGARIS} 
\end{figure}
